Modeling memory and taxis to analyze migrations

### 2021-06-23 text/ms.Rmd
Resource example plot
...

The drifting resource differs from the island resource in that the total amount of resource at any given time point is 1 ($\int_X h(x,t) dx = 1$).  This property is attained by distributing the resource as a re-scaled beta distribution, where the shape and scale parameters vary sinusoidally in such a way as to make the standard deviations and means match the desired values of $m_x, m_t, s_x, s_t$ (see appendix for details).

@@

sigma_t, sigma_x, 
epsilon, alpha, 
beta, lambda, 
x_peak = 30, t_peak = 25

@@

- In general, greater values of $\alpha$ (resource following) lead to an improved ability to match the migration,

- Resource peaks with larger spatial extent (high $\sigma_x$) are smaller duration (low $\sigma_t$) are generally better for migration matching, suggesting that broad but short pulses have the strongest impact on the migration memory.

- Larger values of social attraction ($\beta$) generally lead to poorer migration matching except in those cases where the sociality scale $\lambda$ was high.  Thus, for example, at $\lambda = 20$, no simulations at $\beta >= 200$ managed to acquire or maintain a matched migration.  However, at $\lambda = 50$ or $100$, the migration was slightly better matched at high values of $\beta.  (Fig. **X**)

- Higher diffusion rate

>>>>

The drifting resource differs from the island resource in that the total amount of resource at any given time point is 1 ($\int_X h(x,t) dx = 1$).  This property is attained by distributing the resource as a re-scaled beta distribution, where the shape and scale parameters vary sinusoidally in such a way as to make the standard deviations and means match the desired values of $m_x, m_t, s_x, s_t$ (see appendix for details).  Both types of resources are illustrated in Figure 1.

@@

An illustration of the ability to adjust its migration to find a stable, migratory state that matches the dynamics of the resource is illustrated in Figure X.  Under many combinations of parameters, this kind of steady state adjustment is obtained and maintained.

@@

In general, greater values of $\alpha$ (resource following) lead to an improved ability to match the migration,

Resource peaks with larger spatial extent (high $\sigma_x$) are smaller duration (low $\sigma_t$) are generally better for migration matching, suggesting that broad but short pulses have the strongest impact on the migration memory.

Larger values of social attraction ($\beta$) generally lead to poorer migration matching except in those cases where the sociality scale $\lambda$ was high.  Thus, for example, at $\lambda = 20$, no simulations at $\beta >= 200$ managed to acquire or maintain a matched migration.  However, at $\lambda = 50$ or $100$, the migration was slightly better matched at high values of $\beta.  (Fig. **X**)

Higher diffusion rates
